---
  output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

  ```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE
)
```

# tdfData

An R package containing stage data for each edition of the Tour de France (1903 - 2021).

## Install
Install using

```r
# install.packages("devtools")
devtools::install_github("odaniel1/tdfData")
```

## About the Data

The R package contains a single dataset `tdf_stages`, summarised below:

  ```{r, echo = FALSE}
library(tdfData)
library(tidyverse)
library(knitr)
library(kableExtra)

dat_summary <- tibble(
  Field = names(tdf_stages),
  Class = map(tdf_stages[1,], class),
  Example = tdf_stages[1,]  %>% unlist
)

dat_summary[2,3] <- as.character(as.Date(as.numeric(dat_summary[2,3]), origin = "1970-01-01"))

kable(dat_summary)
```

With the exception of Latitude/Longitude values, all data has been obtained from Wikipedia.

The Latitude/Longitude values have been obtained through geocoding, using the R `tidygeocoder` package. Locations that have been flagged as being outside of France in the Wikipedia table have been given `NA` Latitude/Longitude values.

There are some data quality issues with the matched coordinate values: for instance Stage 2 of the 2010 Tour is marked as starting in *Rotterdam*, not *Rotterdam (Netherlands)*. The geocoding then tries to match this to a location in France, landing on *Rue de Rotterdam, Tours*.

## Example

An animated plot using this data is available (with code) [here](https://odaniel1.github.io/posts/2021-06-25-tdf-shape-21/). The example below creates a simple static plot.

```{r}
library(tdfData)
library(ggplot2)

ggplot(tdf_stages) +
  # background map of france (coord_map fixes the aspect ratio)
  geom_polygon(
    data = map_data("france"), aes(x=long, y = lat, group = group),
    fill = "#f3be02", color = "#f6f4e6", size = 0.1
  ) +
  coord_map() +

  # stage start and finish locations as points
  geom_point(aes(x=`Start Longitude`,y=`Start Latitude`), color = "#2B8C40", alpha = 0.7) +
  geom_point(aes(x=`Finish Longitude`,y=`Finish Latitude`), color = "#F84B30", alpha = 0.7) +
  theme_void() +
  ggtitle("Tour de France Stage Start (Green) and Finish (Red) Locations\n1903 - 2021")
```


